Growing Up with Nell: A Narrative Interface for Literacy

### 2012-03-12 paper.tex
Rewrite the conflict-resolution section.

Story modules can be inherited and extended, as shown in the figure.
This makes it easy to take an existing story and modify it to
better suit particular interests or a particular type of learner, or
just to add variety.  This can lead to conflicts: multiple versions of
a story, or variant scenes within a story, may have their
preconditions satisfied simultaneously.

Conflicts are resolved by consulting a \textit{group} associated with
each scene.  Each group has a default priority and names a scene to be
invoked when a conflict exists; the actions associated with that scene
will temporarily alter the priorities of the conflicting scenes to
resolve the conflict.  For example, the \textit{story-intro-group}
used in Fig.~\ref{fig:rules} defaults to a lower priority, such that
continuing a story in progress is preferred to beginning a new scene.
The resolution scene for \textit{story-intro-group} may be part of its
own story: for example, it may bring us to the controls of a magic airship
which allows us to pilot between locations corresponding to the
various story continuations.  Selecting a destination location bumps
the priority of the given scene allowing us to transition to it
without further conflict.

Other rule groups may invoke random selection or select between stories
based on child preferences, curriculum, or inferred learning style.

Nell's integrated story editor has not yet been implemented.  Its
design is patterned after the Wide Ruled authoring tool, which was
successfully used by non-technical story creators~\cite{skorupski:2009}.

>>>>

Story modules can be inherited and extended, as shown in the figure.
This makes it easy to take an existing story and modify it to
better suit particular interests, a particular type of learner---or
just to add variety.  This can lead to conflicts: multiple versions of
a story, or scenes within a story, may have their
preconditions satisfied simultaneously.

Conflicts are resolved by consulting a \textit{group} associated with
each scene.  Each group has a default priority and names a scene to be
invoked when a conflict exists; the actions associated with that scene
will (eventually) alter the priorities of the conflicting scenes to
resolve the conflict.  The resolution scene may include any number of
actions.  It may select randomly, or based a selection on
child preferences, curriculum progress, or inferred learning style.
The resolution scene may even initiate a new multi-scene story.

For example, the \textit{story-intro-group}
used in Figure~\ref{fig:rules} defaults to a low priority so that
continuing a story in progress is preferred over starting a new story.
When the story in progress is complete, several new story openers will be in
conflict.  The resolution scene for \textit{story-intro-group} brings us
to the controls of a magic airship which flies between locations
corresponding to the various story continuations.  Eventually the
child decides to fly to Mathland to hear the next episode in her
agent Mathis' adventure, and that episode's priority is bumped to
allow us to transition to it without further conflict.

We plan to write an integrated story editor for Nell.  Our model will
be the Wide Ruled authoring tool, which was successfully used by
non-technical story creators~\cite{skorupski:2009}.
